\section{INTRODUCTION}

\subsection{Overview}
The aim of this project is to provide universities, schools and colleges with a
complete solution for its needs of managing data of different aspects of the
organization such as student information, their results, leave, attendance etc,
lecturers information, their attendance, leave, their subjects etc. It is a
web-based solution that provides a simple and intuitive user interface that is
easy to understand. It was created for the university and its affiliated
institutions to conduct, monitor, and analyze complicated activities such as
student admission, examinations, attendance, subject management, assigning
subjects to lecturers, requesting and assigning of leave, adding attendance and
much more.

This project aims to provide a secure and reliable platform where the university
students can login with their user id's and passwords and see their marks,
attendance, subjects and know details about their academics. Professors of the
university can also login with their user id's and passwords and look at the
subjects that they are teaching, track progress of their teachings and also
update the details of exams as well as exam marks of all the students taking
their subject.

\subsection{Purpose}
Institutions mostly use manual methods for keeping records of different aspects
of the institution, they do this by employing people who store the information
in registers, this method is fine for small amounts of information but as the
institutions grow in size; there will be a lot of information that has to be
kept record of and can overwhelm a single person; and hence many people will be
employed for this purpose; this increases chances of errors and also wastes
resources such as time and money, by using digital means for record keeping we
can save time while at the same time reduce a lot of manually caused errors.

\subsection{Scope}
The following are the main scopes of the proposed ERP solution:
\begin{enumerate}
    \item Provide optimal efficiency.
    \item Elimination of duplicate data during entry process.
    \item Help in entering correct information in correct fields.
    \item Integrating with results systems to provide automated results.
\end{enumerate}
