\section{SYSTEM ANALYSIS}

\subsection{Existing System}

The general way in which universities and institutions manage the data that they
handle of different aspects, they usually do it manually and this manual process
it very error prone and time consuming. Also this system is inherently wrong as
it has only one person as the source of truth who can add and manipulate data in
the system, and also the only person who knows where to find the required
information and only that person has to be concerned if any of the data is
required.

This causes a lot of problem, such as, what if the person is unavailable for
some reason, what if the person makes a mistake in entering data, what if he
does not do his job properly and has a lot of data missing from the system. All
of these are inherently the problems that this project tries to solve.

\subsection{Proposed System}

This project improves the organization of work of the institution and reduces
the number of paperwork which is often the waste of time and resources. First
of all it enables students find out the information about the courses,
subjects, required disciplines, the timetable, etc. Moreover, there are always
databases which contain all the information about student’s success and
failures, as all the points and marks are registered in the system. The main
advantage of the university management system is its convenience and speed.

One can find all the necessary data about the university and the educational
process very fast and will not have to travel much to visit the university
himself and ask for consultation there. Moreover, this system makes the
educational process more open and fair, because no one can have any influence
on the data registered in the system and alter it
